Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Jupiter-Sized Planet in IC~2602

### 2020-06-23 paper/authors.tex
minor
restructure paper
update manuscript

%
% key contributions
%

\author[0000-0002-0514-5538]{L. G. Bouma}
\affiliation{Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}

\author[0000-0002-9158-7315]{R. Brahm}
\affiliation{Center of Astro-Engineering UC, Pontificia Universidad
Cat\'olica de Chile, Av. Vicu\~na Mackenna 4860, 782-0436 Macul,
Santiago, Chile}
\affiliation{Instituto de Astrof\'isica, Facultad de F\'isica,
Pontificia Universidad Cat\'olica de Chile, Av. Vicu\~na Mackenna
4860, 782-0436 Macul, Santiago, Chile}
\affiliation{Millennium Institute of Astrophysics, Av. Vicu\~na
Mackenna 4860, 782-0436 Macul, Santiago, Chile}

@@

@@

@@

%PENDING
\author[0000-0002-7595-0970]{C.~.G.~Tinney}
\affiliation{Exoplanetary Science at UNSW, School of Physics, UNSW
Sydney, NSW 2052, Australia}
\affiliation{Australian Centre for Astrobiology, UNSW Sydney, NSW
2052, Australia}

@@

%
% UToyko team
%
%PENDING
\author[0000-0002-4881-3620]{J. Livingston}
\affiliation{Department of Astronomy, University of Tokyo, 7-3-1
Hongo, Bunkyo-ky, Tokyo 113-0033, Japan}

%
% MPIA team
%
%PENDING
\author{T. Henning}
\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17,
69117 Heidelberg, Germany}

%PENDING
\author[0000-0002-5389-3944]{A. Jord\'an}
\affiliation{Facultad de Ingenier\'ia y Ciencias, Universidad Adolfo
Ib\'a\~nez, Av.\ Diagonal las Torres 2640, Pe\~nalol\'en, Santiago,
Chile}
\affiliation{Millennium Institute of Astrophysics, Av. Vicu\~na
Mackenna 4860, 782-0436 Macul, Santiago, Chile}

%PENDING
\author[0000-0001-9513-1449]{N. Espinoza}
\affil{Space Telescope Science Institute, 3700 San Martin Drive,
Baltimore, MD 21218, USA}

@@

\author{TSO/SPOC/POC representatives}

>>>>

%
% key contributions
%
\author[0000-0002-0514-5538]{L. G. Bouma}
\affiliation{Department of Astrophysical Sciences, Princeton
University, 4 Ivy Lane, Princeton, NJ 08540, USA}

@@

%PENDING (MPIA)
\author{P. Sarkis} %Paula sarkis@mpia.de PI of FEROS time
\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, Heidelberg 69117, Germany }

@@

%PENDING
\author[0000-0002-4881-3620]{J. Livingston}
\affiliation{Department of Astronomy, University of Tokyo, 7-3-1
Hongo, Bunkyo-ky, Tokyo 113-0033, Japan}

@@

%PENDING
\author[0000-0002-7595-0970]{C.~G.~Tinney}
\affiliation{Exoplanetary Science at UNSW, School of Physics, UNSW
Sydney, NSW 2052, Australia}
\affiliation{Australian Centre for Astrobiology, UNSW Sydney, NSW
2052, Australia}

%
% WINE MPIA team
%

\author{T. Henning} %Thomas henning@mpia.de FEROS, WINE board
\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, Heidelberg 69117, Germany }

\author[0000-0002-9158-7315]{R. Brahm} %rafael.brahm@uai.cl coordination, WINE board
\affiliation{Facultad de Ingeniería y Ciencias, Universidad Adolfo Ib\'a\~nez, Av.\ Diagonal las Torres 2640, Pe\~nalol\'en, Santiago, Chile}
\affiliation{Millennium Institute for Astrophysics, Chile}

\author[0000-0001-9513-1449]{N. Espinoza} %N\'estor nespinoza@stsci.edu WINE board
\affiliation{Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA}

\author[0000-0002-5389-3944]{A. Jord\'an} %andres.jordan@gmail.com WINE board
\affiliation{Facultad de Ingeniería y Ciencias, Universidad Adolfo Ib\'a\~nez, Av.\ Diagonal las Torres 2640, Pe\~nalol\'en, Santiago, Chile}
\affiliation{Millennium Institute for Astrophysics, Chile}

\author{M. Barbieri} %Maruo mauro.barbieri@uda.cl FEROS observations
\affiliation{INCT, Universidad de Atacama, calle Copayapu 485, Copiap\'o, Atacama, Chile}

\author{S. Nandakumar} %sangeetha.nandakumar@postgrados.uda.cl  FEROS observations
\affiliation{INCT, Universidad de Atacama, calle Copayapu 485, Copiap\'o, Atacama, Chile}

\author{T. Trifonov} %Trifon trifonov@mpia.de FEROS observations
\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, Heidelberg 69117, Germany }

\author{J. Vines} %Jose jose.vines.l@gmail.com FEROS observations
\affiliation{Departamento de Astronom\'ia, Universidad de Chile, Camino El Observatorio 1515, Las Condes, Santiago, Chile}

\author{M. Vuckovic} %Maja maja.vuckovic@uv.cl FEROS observations
\affiliation{Instituto de F\'isica y Astronom\'ia, Universidad de Vapara\'iso, Casilla 5030, Valpara\'iso, Chile}

@@

@@

\author{ASTEP400 collaboration}
\author{TSO/SPOC/POC representatives}
